### 2025-12-15 CV2/papers.tex
update website

\textbf{\href{https://arxiv.org/abs/2411.14601}{On Linear Convergence in Smooth Convex-Concave Bilinearly-Coupled Saddle-Point Optimization: Lower Bounds and Optimal Algorithms}} (Ekaterina Borodich, Dmitry Kovalev). \textit{International Conference on Machine Learning}, 2025.

@@

\textbf{\href{https://www.tandfonline.com/doi/abs/10.1080/10556788.2023.2280062}{Decentralized saddle point problems via non-Euclidean mirror prox}} (Alexander Rogozin, Aleksandr Beznosikov, Darina Dvinskikh, Dmitry Kovalev, Pavel Dvurechensky, Alexander Gasnikov). \textit{Optimization Methods and Software}, 2024.

@@

\textbf{\href{https://link.springer.com/rwe/10.1007/978-3-030-54621-2_860-1}{Decentralized convex optimization over time-varying graphs}} (Alexander Rogozin, Alexander Gasnikov, Aleksander Beznosikov, Dmitry Kovalev). \textit{Encyclopedia of Optimization}, 2023.

@@

@@

\textbf{\href{https://arxiv.org/abs/2503.06628}{On Solving Minimization and Min-Max Problems by First-Order Methods with Relative Error in Gradients}} (Artem Vasin, Valery Krivchenko, Dmitry Kovalev, Fedyor Stonyakin, Nazari Tupitsa, Pavel Dvurechensky, Mohammad Alkousa, Nikita Kornilov, Alexander Gasnikov). \textit{arXiv preprint arXiv:2503.06628}, 2025.

@@

\textbf{\href{https://arxiv.org/abs/2307.12946}{Optimal algorithm with complexity separation for strongly convex-strongly concave composite saddle point problems}} (Ekaterina Borodich, Georgiy Kormakov, Dmitry Kovalev, Aleksandr Beznosikov, Alexander Gasnikov). \textit{arXiv preprint arXiv:2307.12946}, 2023.

>>>>

\textbf{\href{https://arxiv.org/abs/2411.14601}{On Linear Convergence in Smooth Convex-Concave Bilinearly-Coupled Saddle-Point Optimization: Lower Bounds and Optimal Algorithms}} (Ekaterina Borodich, Alexander Gasnikov, Dmitry Kovalev). \textit{International Conference on Machine Learning}, 2025.
\textbf{\href{https://www.tandfonline.com/doi/abs/10.1080/10556788.2023.2280062}{Decentralized saddle point problems via non-Euclidean mirror prox}} (Alexander Rogozin, Aleksandr Beznosikov, Darina Dvinskikh, Dmitry Kovalev, Pavel Dvurechensky, Alexander Gasnikov). \textit{Optimization Methods and Software}, 2025.
\textbf{\href{https://www.tandfonline.com/doi/abs/10.1080/10556788.2025.2545846}{Near-optimal algorithm with complexity separation for strongly convex-strongly concave composite saddle point problems}} (Ekaterina Borodich, Georgiy Kormakov, Dmitry Kovalev, Aleksandr Beznosikov, Alexander Gasnikov). \textit{Optimization Methods and Software}, 2025.

@@

@@

\textbf{\href{https://arxiv.org/abs/2210.09719}{Decentralized convex optimization over time-varying graphs}} (Alexander Rogozin, Alexander Gasnikov, Aleksander Beznosikov, Dmitry Kovalev). \textit{Encyclopedia of Optimization}, 2023.

@@

\textbf{\href{https://arxiv.org/abs/2511.11466}{Non-Euclidean SGD for Structured Optimization: Unified Analysis and Improved Rates}} (Dmitry Kovalev, Ekaterina Borodich). \textit{arXiv preprint arXiv:2511.11466}, 2025.

@@

\textbf{\href{https://arxiv.org/abs/2503.06628}{On solving minimization and min-max problems by first-order methods with relative error in gradients}} (Artem Vasin, Valery Krivchenko, Dmitry Kovalev, Fedyor Stonyakin, Nazarii Tupitsa, Pavel Dvurechensky, Mohammad Alkousa, Nikita Kornilov, Alexander Gasnikov). \textit{arXiv preprint arXiv:2503.06628}, 2025.

@@
